DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-04 paper/main.tex
Change paper to ECRTS format

%
%  $Author: ienne $
%  $Date: 1995/09/15 15:20:59 $
%  $Revision: 1.4 $
%

% \documentclass[10pt,journal,cspaper,compsoc]{IEEEtran}   %%%tc version
\documentclass[10pt, conference]{IEEEtran}
%\documentclass[conference,compsoc]{IEEEtran}
%\documentclass[10pt, conference]{IEEEtran}
%\documentclass[times, 10pt,onecolumn]{article}
\usepackage{amsmath, amssymb, enumerate}

%%%%%%%%%%%%%%%% page control%%%%%%%%%%%%%%%%%
%\usepackage[margin=0.75in]{geometry}

%\linespread{0.991}  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% this is really useful
%\usepackage{cite}
\usepackage{fancybox}
\usepackage{amsfonts}
%\usepackage{algorithm}
%\usepackage[noend]{algorithmic}
\usepackage[usenames]{color}
%\usepackage{colortbl}
%\usepackage[ figure, boxed, vlined]{algorithm2e}
%\usepackage[linesnumbered,vlined]{algorithm2e}
%\usepackage[lined,boxed]{algorithm2e}
\usepackage{listings}

\usepackage[linesnumbered,vlined]{algorithm2e}
\usepackage{graphicx}
\usepackage{times}
\usepackage{psfrag}
\usepackage{subfigure}
\usepackage{caption}
%\usepackage{subcaption}
\usepackage{multirow}
%\usepackage{setspace}
%\usepackage{listings}
\usepackage{epsfig}
%\usepackage{epstopdf}
%\usepackage[font=small,labelfont=bf]{caption}
\usepackage{url}

\usepackage{color}
\def\fixme#1{\typeout{FIXED in page \thepage : {#1}}
%\bgroup \color{red}{} \egroup}
\bgroup \color{red}{[FIXME: {#1}]} \egroup}

\usepackage[pdftex]{hyperref}
\usepackage{rotating,tabularx}

\interfootnotelinepenalty=10000

%% Define a new 'leo' style for the package that will use a smaller font.
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother

%\documentstyle[times,art10,twocolumn,latex8]{article}

%-------------------------------------------------------------------------
% take the % away on next line to produce the final camera-ready version
\pagestyle{plain}
%\thispagestyle{empty}
%\pagestyle{empty}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}

%% remaining budget share, used in task stall section.
\newcommand{\bottomrule}{\hline}
\newcommand{\toprule}{\hline}
\newcommand{\midrule}{\hline}
%-------------------------------------------------------------------------
\begin{document}

\title{DeepPicar:​ ​A​ ​Low-cost​ ​Deep​ ​Neural​ ​Network-based​ ​Autonomous​ ​Car}
\author{Michael Garrett Bechtel, Elise McEllhiney, Heechul Yun\\
\{m783b224, e908m429, heechul.yun\}@ku.edu\\
University of Kansas, USA\\ 
}

@@

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{comparison}
% \input{related}
\input{conclusion}
%-------------------------------------------------------------------------
\bibliographystyle{abbrv}
\bibliography{reference}

>>>>

\documentclass[a4paper,UKenglish]{lipics-v2016}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
% for section-numbered lemmas etc., use "numberwithinsect"

\usepackage{microtype}%if unwanted, comment out or use option "draft"

%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory

\bibliographystyle{plainurl}% the recommended bibstyle

% Author macros::begin %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car}
\titlerunning{DeepPicar: A Low-cost Autonomous Car} %optional, in case that the title is too long; the running title should fit into the top page column

%% Please provide for each author the \author and \affil macro, even when authors have the same affiliation, i.e. for each author there needs to be the  \author and \affil macros
\author[1]{Michael G. Bechtel}
\author[2]{Elise McEllhiney}
\author[3]{Heechul Yun}
\affil[1]{University of Kansas, Lawrence, United States\\
  \texttt{m783b224@ku.edu}}
\affil[2]{University of Kansas, Lawrence, United States\\
  \texttt{e908m429@ku.edu}}
\affil[3]{University of Kansas, Lawrence, United States\\
  \texttt{heechul.yun@ku.edu}}
\authorrunning{M.\,G. Bechtel, E. McEllhiney, H. Yun} %mandatory. First: Use abbreviated first/middle names. Second (only in severe cases): Use first author plus 'et. al.'

\Copyright{Michael G. Bechtel, Elise McEllhiney, Heechul Yun}%mandatory, please use full first names. LIPIcs license is "CC-BY";  http://creativecommons.org/licenses/by/3.0/

\subjclass{Dummy classification -- please refer to \url{http://www.acm.org/about/class/ccs98-html}}% mandatory: Please choose ACM 1998 classifications from http://www.acm.org/about/class/ccs98-html . E.g., cite as "F.1.1 Models of Computation". 
\keywords{Dummy keyword -- please provide 1--5 keywords}% mandatory: Please provide 1-5 keywords
% Author macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{Sebastian Altmeyer}
\EventNoEds{1}
\EventLongTitle{30th Euromicro Conference on Real-Time Systems (ECRTS 2018)}
\EventShortTitle{ECRTS 2018}
\EventAcronym{ECRTS}
\EventYear{2018}
\EventDate{July 3--6, 2018}
\EventLocation{Barcelona, Spain}
\EventLogo{}
\SeriesVolume{XX}
\ArticleNo{YY}
% Editor-only macros::end %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

%-------------------------------------------------------------------------
\input{intro}
\input{background}
\input{overview}
\input{evaluation}
\input{comparison}
% \input{related}
\input{conclusion}
%-------------------------------------------------------------------------
%\bibliographystyle{abbrv}
\bibliography{reference}
